Inference in Hidden Markov Models with Explicit State Duration Distributions

### 2011-10-28 tex/results.tex
added a new graph to describe num transitions visited per iteration, and updated the caption. Haven't put a line in that shows the number of transitions the classical approach would have to take, as it's so large. So I just put it in the caption

\caption{Mean number of transitions visited over the first 1000 iterations of the beam sampler.}
\label{fig:allowed}
\end{figure}

>>>>

\caption{Mean number of transitions visited over the first 1000 iterations of the beam sampler after burn-in. Note that the standard approach would need to examine $((K-1)T)^2 = 10^6$ transitions per time point to achieve similar accuracy.}
\label{fig:allowed}
\end{figure}
